*Platynereis dumerilii* three-day-old connectome --- cell-type compendium

### 2024-10-25 supplements/celltype_compendium_website/index.qmd
Ms and fig, source data upload

# catmaid connection
#conn_http1 <- catmaid_login(
#  server="https://catmaid.jekelylab.ex.ac.uk/", 
#  authname="AnonymousUser",
#  config=httr::config(ssl_verifypeer=0, http_version=1)
#)

# catmaid connection, needs username, password AND token - weird!
{
  # can run this separate file using source function
  conn <- source("~/R/conn.R")
  #for larger calls we need to use http/1, see https://www.gitmemory.com/issue/natverse/rcatmaid/158/641537466
  #for this we configure to http/1.1
#  conn_http1 = catmaid_login(conn=conn, config=httr::config(ssl_verifypeer=0, http_version=1))
}
```

>>>>

# catmaid connection, needs username, password AND token - weird!
{
  # can run this separate file using source function
  conn <- source("~/R/conn.R")
  #for larger calls we need to use http/1, see https://www.gitmemory.com/issue/natverse/rcatmaid/158/641537466
  #for this we configure to http/1.1
  conn_http1 = catmaid_login(conn=conn, config=httr::config(ssl_verifypeer=0, http_version=1))
}
